\documentclass[11pt,letter,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{black}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{url}

\firstname{Samuel A.}
\familyname{Mercier}
%% \title{Résumé}
%%\address{2809 Covington St.}{West Lafayette, IN 47906}
%\mobile{+1~(765)-237-9542}
\email{smercier@purdue.edu}
\homepage{samercier.com}
\social[github]{samontea}
%\photo[64pt][0.4pt]{picture}


\addtolength{\voffset}{-50pt}
\addtolength{\textheight}{150pt}
\addtolength{\hoffset}{-35pt}
\addtolength{\textwidth}{70pt}

%% Body
\begin{document}
\makecvtitle
\vspace{-40pt}
\section{Education}
\cventry{May 2020}{B.S. in Mathematics, B.S. in Computer Science Minor: Philosophy}{Purdue University ({\small College of Science, Honors College})}{West Lafayette, IN}{}{}
\cvitem{}{\emph{Relevant Course Work} CS 381 \textit{Intro to Algorithm Analysis}, CS 252 \textit{Systems Programming}, MA 572 \textit{Algebraic Topology}, MA 553 \textit{Algebra}}
\cvitemwithcomment{}{\textbf{Awards:}
  Purdue Presidential Scholarship \& Purdue Marquis Scholarship}{Fall 2015--Present}
\cvitemwithcomment{}{Thomas Arai Scholarship}{Spring 2019}
\cvitemwithcomment{}{Mitch Daniels Early Graduate Scholarship}{Fall 2015}
\cvitemwithcomment{}{\textbf{Honors:} Dean's List}{6 of 7 semesters}
\cvitemwithcomment{}{The Outstanding Senior Mathematics Major}{Spring 2019}


\section{Experience}
\subsection{\textbf{Work Experience -- Software Engineering}}
\cvitem{}{\textbf{Programming Languages/Frameworks}}
\cvlistdoubleitem{Proficient: C/C++ \& JavaScript}{Familiar: Elixir, Emacs Lisp, Java, Python, \& Ruby}

\cvitemwithcomment{}{\textbf{Software Engineer Intern} Affirm (San Francisco) -- Risk Engineering Team}{September 2019--November 2019}
Expanded the functionality of the underwriting microservice.
Made loan decision tasks asynchronous.
Expanded integration testing of loan decisioning.
\\
\textit{Technologies:} Python, SQL, Shell scripting, \& Docker.
\\
\cvitemwithcomment{}{\textbf{Software Engineer Intern} MongoDB (New York) -- Query Team}{May 2018--August 2018 \& May 2019--Present}
Implemented a new index type which can index all fields of all documents in a given collection.
Sped up \$lookup/join queries by 28x according to performance tests.
Recovered technical debt by rearchitecting projection execution.
\\
\textit{Technologies:} C++, Python (for testing), \& JavaScript (for testing).
\\
\cvitemwithcomment{}{\textbf{Software Engineer Intern} MongoDB (New York) -- Monitoring Team}{May 2017--August 2017}
Researched and implemented time series analysis techniques for anomaly detection for their ``DaaS'' platform. Integrated into existing alerts framework to create automated anomaly detection alerts.
\\
\textit{Technologies:} Java \& MongoDB.
\\
\cvitemwithcomment{}{\textbf{Web Development Intern in Support of NASA Systems Engineering} NASA JSC}{January 2017--May 2017}
Developed requirement management software used throughout NASA.
Isolated state, and added routing.
\\
\textit{Technologies:} JavaScript, Node, Angular 1.x, Brunch, \& Redux.
\\
\cvitemwithcomment{}{\textbf{Software Engineer Intern Fullstack} Springbuk (Indianapolis)}{June 2016--August 2016}
Led development on an external onboarding application.
Improved frontend/backend communication of product.
\\
\textit{Technologies:} PostgreSQL with ActiveRecord as a wrapper, Ruby, Ruby on Rails, \& JQuery.
\subsection{\textbf{Work Experience -- Teaching}}
\cvitemwithcomment{}{\textbf{MA 161/162 Undergraduate Teaching Assistant}}{August 2018--Present}
Answer questions with students in ``flipped classroom'' for MA 161/162 (\textit{Calculus I/II}).
\\
\cvitemwithcomment{}{\textbf{CS 252 Undergraduate Teaching Assistant}}{January 2018--May 2018 \& August 2018--Present}
Assist in teaching CS 252 \textit{Systems Programming} in weekly lab classes \& preparing materials (labs, exams, etc.)
\\
\cvitemwithcomment{}{\textbf{CS 240 Undergraduate Teaching Assistant}}{January 2016--May 2016 \& August 2016--December 2016}
Assist in teaching CS 240 \textit{Programming in C} in weekly lab classes \& preparing materials (labs, exams, etc.)
\\
\cvitemwithcomment{}{\textbf{CS USB Help Room Tutor}}{September 2015--December 2015}
Tutored in CS 180 \textit{Object-Oriented Programming} \& CS 240 \textit{Programming in C}.
\subsection{\textbf{Volunteer Experience}}
\cvitemwithcomment{}{\textbf{BoilerMake Hackathon Executive Board} (Dev \& User Experience Team)}{January 2016--October 2018}
Helped plan and organize anything relating to resources/services for the event participants.
Made \href{https://github.com/BoilerMake/puzzles-BM4}{\underline{a puzzle webapp}}.
\\
\cvitemwithcomment{}{\textbf{Purdue FIRST Programs} (IT Team)}{August 2015--December 2016}
\cvitemwithcomment{}{IT Director}{May 2016--December 2016}
Lead IT work for organization that helps support local robotics teams in high schools and middle schools.
%%Led development of a home brewed content management system.
%%\textit{Technologies:} Elixir, Phoenix, React, \& Redux.
%%\\
%\cvitemwithcomment{}{\textbf{FIRST Robotics Team 461--Westside Boiler Invasion}}{2012--2015}
%Programmed the robot in C/C++ junior year.
%\url{https://github.com/frc461/rowdy-16}
%\\
%Made a scouting system for recording data on other teams that consisted of a Node-Webkit application for data entry \& viewing and a C program that processed and summarized the data sophomore year.
%\\
%Led development on a website in Rails freshman year. \url{http://github.com/frc461/website-2013}
%\\
%\cvitem{}{\textbf{Projects}}
%\cvlistitem{\textbf{\url{https://github.com/samontea/todoish}} -- A todo list web app with a lot of the features I like from Todoist.}
%\cvlistitem{\textbf{\url{https://github.com/samontea/pace}} -- A lightweight elixir performance analysis library.}
\end{document}
